\clearpage
# Appendix

## Rebuilding strategies with catches constrained by the ABC{#abc-max-strategies}

Altenative rebuilding alternative that cap the potential removals across alternative strategies by the ABC Rule with time-varying $\sigma$ values.  Capping removals by the ABC in this manner impacts both the SPR = 0.55 and the $\text{T}_\text{MID}$ (SPR = 0.545) rebuilding strategies where projected catches from these strategies equal those from the ABC Rule.  The intermediate rebuilding strategies, SPR between 0.60 - 0.75, are not impacted by applying a removal cap tied to the ABC values.    


```{r, results = 'asis'}
# Rebuilding Reference Points Table

quants = c(round(reb[[4]]$sb0,2), 
		   round(reb[[4]]$sb40, 2), 
		   round(reb[[4]]$sb_ass_year, 2),
		         reb[[4]]$recovery_spec[4],
		         reb[[4]]$recovery_spec[3], 
		         reb[[4]]$tmin + reb[[4]]$recovery_spec[4], 
		         reb[[4]]$mean_gen, 
		         reb[[4]]$tmax, 
		   "TBD",
		   "TBD")

row_names = c("SB0 (millions of eggs)", "SB40% (millions of eggs)", 
			"SB2021 (millions of eggs)", "Year rebuilding begins",
		    "Current year", "Tmin", "Mean generation time (years)", "Tmax", 
		    "Ttarget", "SPRtarget")

col_names = c("Parameter", "2021 Assessment Values")
out = cbind(row_names, quants)

table_format(x = out,
             caption = "Summary of the rebuilding reference points.",
             label = "ref-points-no-abc-cap",
             align = 'l',
             col_names = col_names)
```

\clearpage

```{r, results = 'asis'}
# Rebuilding Reference Points Table

quants = rbind(round(reb[[4]]$acl_matrix[1:4,-1],2),
		             reb[[4]]$rebuild_quants$SPR,
		             reb[[4]]$rebuild_quants$Ttarget,
		             rep(reb[[4]]$tmax, length(reb[[1]]$rebuild_quants$Ttarget)),
		             reb[[4]]$rebuild_quants$Prebuild) # Prob by Tmax

row_names = c("2021 Assumed Removals (mt)", 
			  "2022 Assumed Removals (mt)",
			  "2023 ACL (mt)", "2024 ACL (mt)", "SPR", "Ttarget", 
			  "Tmax",
			  "Probability of recovery by Tmax")
out = cbind(row_names, quants)
col_names = c("", colnames(out)[-1])

table_format(x = out,
             caption = "Results of rebuilding alternatives based on selection of an SPR target or year for 50 percent probability of recovery based on the assumed removals for 2021-22. The SPR value provided under the ABC Rule is the realized average applied SPR across projection years based on time-varying sigmas and the applied buffer where the ABC Rule is based initially on an SPR value of 0.50.",
             label = "reb-options-no-abc-cap",
             align = 'l',
             landscape = TRUE,
             col_names = col_names)
```


```{r, results = 'asis'}

out = as.data.frame(round(reb[[4]]$prob_matrix[1:35, ],3))

table_format(x = out,
             caption = "Probability of recovery by year for rebuilding SPR alternatives assuming removals of 90.8 and 88.9 mt in 2021 and 2022, respectively.",
             label = "prob-mat-abc",
             align = 'l',
             col_names = colnames(out))
```


```{r, results = 'asis'}

out = as.data.frame(round(reb[[4]]$acl_matrix[1:35, ],2))

table_format(x = out,
             caption = "Median catches (mt) by year for rebuilding SPR alternatives assuming removals of 90.8 and 88.9 mt in 2021 and 2022, respectively.",
             label = "acl-mat-abc",
             align = 'l',
             col_names = colnames(out))
```


```{r, results = 'asis'}

out = as.data.frame(round(reb[[4]]$ofl_matrix[1:35, ],2))

table_format(x = out,
             caption = "Median ABCs (mt) by year for rebuilding SPR alternatives assuming removals of 90.8 and 88.9 mt in 2021 and 2022, respectively.",
             label = "ofl-mat-abc",
             align = 'l',
             col_names = colnames(out))
```


```{r, results = 'asis'}

out = as.data.frame(round(reb[[4]]$relativeb_matrix[1:35, ],2))

table_format(x = out,
             caption = "Median pawning output relative to the 40 percent of unfished spawning output target by year for rebuilding SPR alternatives assuming removals of 90.8 and 88.9 mt in 2021 and 2022, respectively. ",
             label = "rel-ssb-mat-abc",
             align = 'l',
             col_names = colnames(out))
```

## Rebuilding data file

The rebuild.dat file used for the SPR alternative analysis has been provided as a separate file.