# Introduction

## Basic Information

This assessment reports the status of `r spp` (*Sebastes caurinus*) off the Oregon coast using data through 2020.


```{r, echo=FALSE, results='asis'}
general_wd = "C:/Assessments/2021/copper_rockfish_2021/write_up/general_text"
filein = file.path(general_wd,'1_intro_life_history_fishery_info.Rmd')
read_child(filein)
```

## Historical and Current Fishery Information

Off the coast of Oregon, `r spp` is caught in both commercial and recreational fisheries. The landings from the commercial fishery were minimal until the mid-1960s. Following the development of the nearshore commercial fishery in the late 1990s, Oregon Department of Fish and Wildlife (ODFW) implemented a state-permitted limited access fishery that regulated fleet size, period landing limits and established harvest guidelines [@rodomsky_2019_2020]. `r Spp` is one of 11 species in the Other Nearshore Rockfish category managed under a single state harvest guideline. Within this management category, China, quillback and `r spp` are the three primary species landed. Currently, this commercial fishery is centered on the southern Oregon coast. `r spp` is primarily landed live as a part of this fishery and is one of the predominant rockfish species in this fishery, but some landings are made to the fresh market. `r Spp` is primarily landed on hook and line and bottom longline gears in the commercial fishery. The recreational fishery off the coast of Oregon developed during the 1970s, with the first recorded landings of `r spp` in 1979. Recreational removals have increased across time (Table \ref{tab:allcatches} and Figure \ref{fig:catch}).  

This analysis asseses the stock off the Oregon coast as a separate stock from other populations off the West Coast based on the fairly sedentary nature of `r spp`, which likely limits flow of fish between California and Washington. The substrate of the northern Oregon and southern Washington coast is primarily sandy bottom and combined with the Columbia River plume between Oregon and Washington these factors create a natural separation between the Oregon and Washington populations. Additionally, the exploitation history and magnitude of removals off the Oregon coast has been dramatically lower than removals off the California coast.   


## Summary of Management History and Performance

```{r, echo=FALSE, results='asis'}
general_wd = "C:/Assessments/2021/copper_rockfish_2021/write_up/general_text"
filein = file.path(general_wd,'1_intro_management.Rmd')
read_child(filein)
```
The OFL and ACLs for `r spp` North of 40$^\circ$ 10' Lat. N. management area, the state/specific ACL allocation (49 percent for Oregon, Groundfish Management Team, personal communication), and the total removals are shown in Table \ref{tab:ofl}.
