# Introduction

## Basic Information

This assessment reports the status of `r spp` (*Sebastes caurinus*) off the Oregon coast using data through 2020.


```{r, echo=FALSE, results='asis'}
general_wd = "C:/Assessments/2021/copper_rockfish_2021/write_up/general_text"
filein = file.path(general_wd,'1_intro_life_history_fishery_info.Rmd')
read_child(filein)
```

## Historical and Current Fishery Information

Off the coast of Oregon, `r spp` is caught in both commercial and recreational fisheries. Landings from the commercial fishery were minimal until the mid-1960s. Following the development of the nearshore commercial fishery in the late 1990s, Oregon Department of Fish and Wildlife (ODFW) implemented a state-permitted limited access fishery that regulated fleet size, period landing limits and established harvest guidelines [@rodomsky_2019_2020]. `r Spp` is one of 11 species in the Other Nearshore Rockfish category managed under a single state harvest guideline. Within this management category, China, quillback and `r spp` are the three primary species landed. Currently, this commercial fishery is centered on the southern Oregon coast. `r spp` is primarily landed live as a part of this fishery, but some landings are made to the fresh market. The average sized `r spp` landed in the commercial fishery, live or dead, was 17 inches (43 cm) and around 4 lbs.  with a minimum size limit of 12 inches (30.5 cm) since 2000 (Troy Buell, ODFW, personal communication). `r Spp` are primarily landed on hook and line and bottom longline gears in the commercial fishery. The recreational fishery off the coast of Oregon developed during the 1970s, with the first recorded landings of `r spp` in 1979. Recreational removals have increased across time (Table \ref{tab:allcatches} and Figure \ref{fig:catch}).  

This analysis assesses the stock off the Oregon coast as a separate stock from other populations off the West Coast based on the fairly sedentary nature of `r spp`, which likely limits flow of fish between California and Washington. The substrate of the northern Oregon and southern Washington coast is primarily sandy bottom and combined with the Columbia River plume between Oregon and Washington, these factors create a natural separation between the Oregon and Washington populations. Additionally, the exploitation history and magnitude of removals off the Oregon coast has been dramatically lower than removals off the California coast.   


## Summary of Management History and Performance

```{r, echo=FALSE, results='asis'}
general_wd = "C:/Assessments/2021/copper_rockfish_2021/write_up/general_text"
filein = file.path(general_wd,'1_intro_management.Rmd')
read_child(filein)
```

Table \ref{tab:ofl} shows the Nearshore Rockfish North complex level OFL and ACL, the `r spp` OFL and ACL contribution amounts, the state-specific allocations (49 percent for Oregon, Groundfish Management Team, personal communication) of the `r spp` ACL contribution, and the total removals in Oregon. 
