# Assessment Model

## Summary of Previous Assessments 

```{r, echo=FALSE, results='asis'}
general_wd = "C:/Assessments/2021/copper_rockfish_2021/write_up/general_text"
filein = file.path(general_wd,'model_previous_assess.Rmd')
read_child(filein)
```

### Bridging Analysis


```{r, echo=FALSE, results='asis'}
general_wd = "C:/Assessments/2021/copper_rockfish_2021/write_up/general_text"
filein = file.path(general_wd,'model_bridge.Rmd')
read_child(filein)
```

## Model Structure and Assumptions

The Oregon `r spp` area was assessed using a two-sex model with sex specific life history parameters.  The model assumed two fleets: 1) commercial and 2) recreational fleets with removals beginning in `r startyr`. Selectivity was specified to be asymptotic using the double normal parameterization within Stock Synthesis for the commercial fleet. The ascending slope and size of maximum selectivity parameters were estimated for the commercial fleet.  The recreational fleet also used a double normal parameterization but was allowed to estimate reduced selectivity for the largest fish (i.e., allowed to be dome-shaped). Annual recruitment was assumed to be deterministic within the base model. 

### Modeling Platform and Structure

```{r, echo=FALSE, results='asis'}
general_wd = "C:/Assessments/2021/copper_rockfish_2021/write_up/general_text"
filein = file.path(general_wd,'model_platform.Rmd')
read_child(filein)
``` 

## Model Selection and Evaluation

The base assessment model for `r spp` was developed to balance parsimony and realism, and the goal was to estimate a spawning output trajectory for the population of `r spp` off the Oregon coast. The model contains many assumptions to achieve parsimony and uses many different sources of data to estimate reality. A series of investigative model runs were done to achieve the final base model.


### Priors

```{r, echo=FALSE, results='asis'}
general_wd = "C:/Assessments/2021/copper_rockfish_2021/write_up/general_text"
filein = file.path(general_wd,'model_priors.Rmd')
read_child(filein)
```  

### Data Weighting

Length composition data for the commercial fishery had input sample sizes by year determined from the equation listed in Section \ref{commercial-fishery}. The input sample size for the recreational fishery length composition data was set equal to the number of length samples by year.   

The base  model was weighted using the "McAllister-Ianelli method", that weights data using the harmonic means [@mcallister_bayesian_1997]. The weights applied in the base model are shown in Table \ref{tab:dw}. The McAllister-Ianelli method was selected for the base model based on the lower weight applied to the commercial lengths and higher weight applied to the recreational lengths compared to the other data weighting methods. The model was highly sensitivity to the treatment of the commercial length data (discussed in Sections \ref{para-estimates} and \ref{sensitivities}) and the McAllister-Ianelli data weighting was selected based on model stability and parameter estimates.  Sensitivities were performed examining the difference in weighting using Francis [-@francis_data_2011] and the Dirichlet Multinomial Weighting [-@thorson_model-based_2017].

### Estimated and Fixed Parameters

There were 6 estimated parameters in the base model. These included one parameter for $R_0$ and 5 parameters for selectivity (Table \ref{tab:params}).

Fixed parameters in the model were as follows. Annual recruitment was assumed to be deterministic for all years. Steepness was fixed at `r round(model$parameters[model$parameters$Label == "SR_BH_steep","Value"],2)`, the mean of the rockfish prior. Natural mortality was fixed at `r round(model$parameters[model$parameters$Label == "NatM_p_1_Fem_GP_1","Value"],3)` yr^-1^ for females and males, the median of the prior.   Growth, maturity-at-length, and length-at-weight was fixed as described above in Section \ref{biological-data}. Likelihood profiles were performed across select parameters to examine the information content in the data (see Section \ref{like-profiles}). 

Dome-shaped selectivity was explored for all fleets within the model. Older `r spp` are often found in deeper waters and may move into areas that limit their availability to fishing gear. The final base model estimated dome-shaped selectivity for only the largest fish for the recreational fleet. The selectivity for the commercial fleet was fixed to be asymptotic. During model development no evidence of dome-shaped selectivity for the commercial fleet was found. The ascending width, size at peak, and final selectivity parameters for the double normal parameterization were estimated in the based model for the recreational fleet. The descending width was estimated during model development and fixed in the base model based upon those explorations. The ascending width and the size at peak selectivity of the double normal parameterization was estimated in the base model for the commercial fleet. 

