# Assessment Model

## Summary of Previous Assessments 

```{r, echo=FALSE, results='asis'}
general_wd = "C:/Assessments/2021/copper_rockfish_2021/write_up/general_text"
filein = file.path(general_wd,'model_previous_assess.Rmd')
read_child(filein)
```

### Bridging Analysis

A direct bridging analysis was not conducted because the previous assessment was structured to include the area from North of Point Conception to the Washington/Canadian border.  


## Model Structure and Assumptions

The Oregon `r spp` area was assessed using a two-sex model with sex specific life history parameters.  The model assumed two fleets: 1) commercial and 2) recreational fleets with removals beginning in `r startyr`. Selectivity was specified to be asymptotic using the double normal parameterization within SS for the commercial fleet. The ascending slope and size of maximum selectivity parameters were estimated for the commercial fleet.  The recreational fleet also used a double normal parameterization but was allowed to estimate reduced selectivity for the largest fish (i.e., allowed to be dome-shaped). Annual recruitment deviations were estimated within the base model. 

### Modeling Platform and Structure

```{r, echo=FALSE, results='asis'}
general_wd = "C:/Assessments/2021/copper_rockfish_2021/write_up/general_text"
filein = file.path(general_wd,'model_platform.Rmd')
read_child(filein)
``` 

## Model Selection and Evaluation

The base assessment model for `r spp` was developed to balance parsimony and realism, and the goal was to estimate a spawning output trajectory for the population of `r spp` off the Oregon coast. The model contains many assumptions to achieve parsimony and uses many different sources of data to estimate reality. A series of investigative model runs were done to achieve the final base model.


### Priors

```{r, echo=FALSE, results='asis'}
general_wd = "C:/Assessments/2021/copper_rockfish_2021/write_up/general_text"
filein = file.path(general_wd,'model_priors.Rmd')
read_child(filein)
```  

### Data Weighting

Length composition data for the commercial fishery had input sample sizes by year determined from the equation listed in Section \ref{commercial-fishery}. The input sample size for the recreational fishery length composition data was set equal to the number of length samples by year.   

The base  model was weighted using the "Francis method", which was based on equation TA1.8 in Francis [-@francis_data_2011]. This formulation looks at the mean length or age and the variance of the mean to determine if across years, the variability is explained by the model. If the variability around the mean does not encompass the model predictions, then that data source should be down-weighted. This method accounts for correlation in the data (i.e., the multinomial distribution). The weights applied in the base model are shown in Table \ref{tab:dw}. Sensitivities were performed examining the difference in weighting using McAllister-Ianelli Harmonic Mean Weighting [-@mcallister_bayesian_1997] and the Dirichlet Multinomial Weighting [-@thorson_model-based_2017].

### Estimated and Fixed Parameters

There were 112 estimated parameters in the base model. These included one parameter for $R_0$, 5 parameters for selectivity, 94 recruitment deviations, and 12 forecast recruitment deviations (Table \ref{tab:params}).

Fixed parameters in the model were as follows. Steepness was fixed at `r round(model$parameters[model$parameters$Label == "SR_BH_steep","Value"],2)`, the mean of the rockfish prior. Natural mortality was fixed at `r round(model$parameters[model$parameters$Label == "NatM_p_1_Fem_GP_1","Value"],3)` yr^-1^ for females and males, which is the median of the prior.  The standard deviation of recruitment deviates was fixed at `r round(model$parameters[model$parameters$Label == "SR_sigmaR","Value"],2)`. Growth, maturity-at-length, and length-at-weight was fixed as described above in Section \ref{data}. Likelihood profiles were performed across select parameters to examine the information content in the data. 

Dome-shaped selectivity was explored for all fleets within the model. Older `r spp` are often found in deeper waters and may move into areas that limit their availability to fishing gear. The final base model estimated dome-shaped selectivity for only the largest fish for the recreational fishery. The selectivity for the commercial fishery was fixed to be asymptotic. The ascending and descending width (recrational fleet only) of the double normal selectivity curve were estimated during model development and fixed in the base model based upon those explorations.

