```{r executive, echo = FALSE}
executive <- list()
executive[["stock"]] <- paste0("This assessment reports the status of ",
  spp, " (_", spp.sci, "_) off the ", coast, 
  " coast using data through 2020.")

general_wd <-  'C:/Assessments/2021/copper_rockfish_2021/write_up/general_text'
```
# Executive Summary{-}
## Stock{-}
`r executive[["stock"]]`

The years is `r endyr`

## Landings{-}
Replace text.

Table \ref{tab:ssb}.

```{r}
tab = read.csv(file.path(mod_loc, "tables", "a_Catches_ES.csv"))
col_names = c("Year", "Recreational (mt)", "Commercial (mt)", "Total Mortality")

table_format(x = as.data.frame(tab),
			caption = 'Removals by fleet for the last 10 years.',
			label = 'mortality',
			digits = c(0,0,2,2),
			longtable = FALSE,
			col_names = col_names,
			align = c('r','c','c','c'))
```

Here is a reference to the catches (Table \ref{tab:mortality})


## Data and Assessment{-}
Replace text.

## Stock Biomass{-}
Replace text.

```{r, results = 'asis'}
tab = read.csv(file.path(mod_loc, "tables", "b_SSB_ES.csv"))
col_names = c("Year", "Spawning Output", "Lower Interval", "Upper Interval", "Fraction Unfished", "Lower Interval", "Upper Interval")

table_format(x = tab,
			caption = 'Estimated spawning output and the fraction unfished and the 95 percent confidence intervals.',
			label = 'ssb',
			longtable = FALSE,
			digits = c(0,0,0,0, 3,3,3),
			#format.args = list(big.mark = ","), 
			col_names = col_names,
			align = c('r', rep('c', ncol(tab) - 1)))

```

Alternative table based on latex file: 

\input{C:/Assessments/2021/copper_rockfish_2021/models/wa/0.0_init_model/tables/b_SSB_ES.tex}

## Recruitment{-}
Replace text.

```{r, results = 'asis'}
tab = read.csv(file.path(mod_loc, "tables", "c_Recr_ES.csv"))
col_names = c("Year", "Recruitment", "Lower Interval", "Upper Interval",  "Recruit Devs.","Lower Interval", "Upper Interval")

table_format(x = tab,
			caption = 'Estimated recruitment and recruitment deviations (recruit devs.) and the 95 percent confidence intervals.',
			label = 'recr',
			longtable = FALSE,
			col_names = col_names,
			digits = c(0,0,0,0, 3,3,3),
			align = c('r', rep('c', ncol(tab) - 1)))

```

## Exploitation Status{-}
Replace text.

```{r, results = 'asis'}
tab = read.csv(file.path(mod_loc, "tables", "d_SPR_ES.csv"))
col_names = c("Year", "1-SPR", "Lower Interval", "Upper Interval", "Exploit. Rate", "Lower Interval", "Upper Interval")

table_format(x = tab,
			caption = 'Estimated 1-SPR in percent and the exploitation rate (Exploit. Rate) and the 95 percent confidence intervals.',
			label = 'expliot',
			longtable = FALSE,
			col_names = col_names,
			digits = c(0, 1,1,1, 3,3,3),
			align = c('r', rep('c', ncol(tab) - 1)))

```

## Reference Points{-}
Replace text.

```{r, results = 'asis'}
library(dplyr)
tab = read.csv(file.path(mod_loc, "tables", "e_ReferencePoints_ES.csv"))
col_names = c("Metric", "Estimate", "Lower Inteval", "Upper Interval")
tab = data.frame(tab)
tab = tab %>% mutate_if(is.numeric, round, digits = 2)

table_format(x = tab,
			caption = 'Reference points',
			label = 'ref',
			longtable = FALSE,
			col_names = col_names,
			align = c('r', rep('c', ncol(tab) - 1)),
			custom_width = TRUE,
            col_to_adjust = 1:3, 
            width = c('6cm', '2cm', '2cm', '2cm'))
```

## Management Performance{-}
Replace text.

```{r, results = 'asis'}
tab = read.csv(file.path(mod_loc, "tables", "f_Manage_ES.csv"))
col_names = colnames(tab)

table_format(x = tab,
			caption = 'The OFL, ABC, ACL, and Landings for the last 10 years.',
			label = 'manage',
			longtable = FALSE,
			col_names = col_names,
			align = c('r','c','c','c','c'))
```


## Unresolved Problems and Major Uncertainties{-}
Replace text.

## Decision Table{-}
Add the projection table

```{r, results = 'asis'}
tab = read.csv(file.path(mod_loc, "tables", "g_Projections_ES.csv"))
col_names = c("Year", "OFL", "ABC", "3+ Biomass", "Spawning Output", "Fraction Unfished")

table_format(x = tab,
			caption = 'Projections',
			label = 'project',
			longtable = FALSE,
			col_names = col_names,
			digits = c(0, 1,1,1,1,3),
			align = c('r',rep('c', ncol(tab) - 1)))
```

Replace text.

## Research and Data Needs{-}
Replace text.


