```{r executive, echo = FALSE}
executive <- list()
executive[["stock"]] <- paste0("This assessment reports the status of ",
  spp, " (_", spp.sci, "_) off the ", coast, 
  " coast using data through xxxx.")
```
# Executive Summary{-}
## Stock{-}
`r executive[["stock"]]`

The years is `r endyr`

## Landings{-}
Replace text.

```{r}
tab = read.csv(file.path(mod_loc, "tables", "a_Catches_ES.csv"))
tab = tab[,1:3]
colnames(tab) = c("Year", "Recreational (mt)", "Commercial (mt)")


options(kableExtra.latex.load_packages = FALSE)
library(kableExtra)

kableExtra::kbl(tab, caption = "Catches!", digits = c(0, 0, 2, 2), label = 'test', align = 'l', booktabs = T) %>%
	kableExtra::kable_styling(latex_options = c('hold_position'), font_size = 11) #%>%   
	#column_spec(2, width = "2em")                   

```
Alterantive formatting using function format_table:

```{r}
tab = read.csv(file.path(mod_loc, "tables", "a_Catches_ES.csv"))
col_names = c("Year", "Recreational (mt)", "Commercial (mt)", "Total Mortality")

table_format(x = as.data.frame(tab),
			caption = 'Formatted catches',
			label = 'mortality',
			digits = c(0,0,2,2),
			longtable = FALSE,
			col_names = col_names,
			align = c('r','c','c','c'))
```


Does this work Table \ref{tab:test} vs. Table \ref{tab:mortality}?



## Data and Assessment{-}
Replace text.

## Stock Biomass{-}
Replace text.

```{r, results = 'asis'}
tab = read.csv(file.path(mod_loc, "tables", "b_SSB_ES.csv"))
col_names = c("Year", "Spawning Output", "CI", "Depletion", "CI")

table_format(x = tab,
			caption = 'Estimated spawning output and relative stock status (depletion) and the 95 percent confidence intervals (CI).',
			label = 'ssb',
			longtable = FALSE,
			col_names = col_names,
			align = c('r','c','c','c','c'))

```

## Recruitment{-}
Replace text.

## Exploitation Status{-}
Replace text.

## Reference Points{-}
Replace text.

## Management Performance{-}
Replace text.

## Unresolved Problems and Major Uncertainties{-}
Replace text.

## Decision Table{-}
Replace text.

## Research and Data Needs{-}
Replace text.
