# Introduction

## Basic Information

This assessment reports the status of `r spp` (*Sebastes caurinus*) off the Washington coast using data through 2020.

```{r, echo=FALSE, results='asis'}
general_wd = "C:/Assessments/2021/copper_rockfish_2021/write_up/general_text"
filein = file.path(general_wd,'1_intro_life_history_fishery_info.Rmd')
read_child(filein)
```

## Historical and Current Fishery Information

Off the coast of Washington State `r spp` is primarily caught in the recreational/sport fishery with very little mortality from commercial fishing (Table \ref{tab:allcatches} and Figure \ref{fig:catch}). `r Spp` has been a target of recreational fishing as early as 1935 with catches stabilizing around 2,500 - 3,000 fish per year starting around 1980 with the exception of select years with high (2005) or low catches (2015). 

`r Spp` has not been targeted by commercial fisheries in Washington waters. Washington closed state waters to commercial fixed gears in 1995 and to trawling in 1999 and the depths preferred by `r spp` are predominantly found within state waters.  In response to the development of the live-fish fishery in California and Oregon, Washington took preemptive action in 1999 to prevent the fishery from developing by prohibiting the landing of live-fish. There are four treaty tribes that fish under separate rules and are not subject to the state water closure.  `r Spp` are usually landed in the Nearshore Rockfish group, a mixed-species market category. Species composition samples were taken from sampled landings and proportions of `r spp` reported in the Nearshore market category are estimated by port, quarter, gear, and year. In 2020, COVID-19 closures of tribal lands prevented samplers from accessing all commercial catch, so an average proportion of `r spp` in 2017 - 2019 was applied to all associated tribal landings. 

The primary region of recreational fishing off the Washington coast occurs in the central to northern regions. These areas have rocky habitat that rockfish species such as `r spp` are associated with in comparison to the southern coast of Washington which consists primarily of soft and sandy substrate.  The stock off the Washington coast was assessed as a separate stock from other populations off the West Coast based on three factors: 1) suspected limited flow of fish between Washington and Oregon given the substrate separation, 2) the different exploitation patterns within Washington waters compared to Oregon and California, and 3) the quantity of length data in Washington compared to other areas.   


## Summary of Management History and Performance
```{r, echo=FALSE, results='asis'}
general_wd = "C:/Assessments/2021/copper_rockfish_2021/write_up/general_text"
filein = file.path(general_wd,'1_intro_management.Rmd')
read_child(filein)
```
The OFL and ACLs for `r spp` North of 40$^\circ$ 10' Lat. N. management area, the state-specific ACL allocation (26 percent for Washington, Groundfish Management Team, pers. comm.), and the total removals are shown in Table \ref{tab:ofl}.
