# Introduction

## Basic Information

This assessment reports the status of `r spp` (*Sebastes caurinus*) off the California coast, north of Point Conception, using data through 2020.

```{r, echo=FALSE, results='asis'}
general_wd = "C:/Assessments/2021/copper_rockfish_2021/write_up/general_text"
filein = file.path(general_wd,'1_intro_life_history_fishery_info.Rmd')
read_child(filein)
```

## Historical and Current Fishery Information

Off the coast of California, north of Point Conception, `r spp` is caught in both commercial and recreational fisheries. Recreational removals have been the largest source of fishing mortality, comprising nearly 85 percent of total removals of `r spp` across all years (Table \ref{tab:allcatches} and Figure \ref{fig:catch}).  The landings from the commercial fishery have been minimal by year, expect for a brief period between the mid-1980s and early-2000s. 

```{r, echo=FALSE, results='asis'}
general_wd = "C:/Assessments/2021/copper_rockfish_2021/write_up/general_text"
filein = file.path(general_wd,'1_intro_ca_commercial.Rmd')
read_child(filein)
```

`r Spp` residing between Point Conception and the California/Oregon border are assessed here as a single, separate stock.  This designation was made based on oceanographic, geographic, and fishery conditions.  The `r spp` population in California waters was split at Point Conception due to water circulation patterns that create a natural barrier between nearshore rockfish populations to the north and south. The northern border for this assessment was defined as the California/Oregon border due to substantial differences in historical and current exploitation levels. Additionally, he fairly sedentary nature of adult `r spp`, likely limits flow of fish between northern California and areas to the north.

## Summary of Management History and Performance

```{r, echo=FALSE, results='asis'}
general_wd = "C:/Assessments/2021/copper_rockfish_2021/write_up/general_text"
filein = file.path(general_wd,'1_intro_management.Rmd')
read_child(filein)
```

Table \ref{tab:ofl} show the Nearshore Rockfish North and South complex level OFLs and ACLs, the `r spp` OFL and ACL contributions amounts for both areas, the state-specific allocations of the `r spp` ACL contribution (the south `r spp` ACL plus 25 percent allocated to California from the north ACL), and the total removals for California, north of Point Conception. 
