# Assessment Model

## Summary of Previous Assessments 

```{r, echo=FALSE, results='asis'}
general_wd = "C:/Assessments/2021/copper_rockfish_2021/write_up/general_text"
filein = file.path(general_wd,'model_previous_assess.Rmd')
read_child(filein)
```

### Bridging Analysis

```{r, echo=FALSE, results='asis'}
general_wd = "C:/Assessments/2021/copper_rockfish_2021/write_up/general_text"
filein = file.path(general_wd,'model_bridge.Rmd')
read_child(filein)
```


## Model Structure and Assumptions

`r Spp` north of Point Conception off the coast of California are assessed using a two-sex model with sex specific life history parameters.  The model assumed two fleets: 1) commercial and 2) recreational with removals beginning in `r startyr`. Selectivity was specified using the double normal parameterization within Stock Synthesis for the commercial fleet where selectivity was fixed to be asymptotic with the ascending slope and size of maximum selectivity parameters being estimated. The commercial fishery estimated two selectivity blocks: one from `r startyr`- 2008 and the second from 2009 - `r endyr`. The recreational fleet also used a double normal parameterization to model selectivity and was fixed to be asymptotic. Annual recruitment deviations were estimated for all years. 

### Modeling Platform and Structure

The assessment was conducted used Stock Synthesis version 3.30.16 developed by Dr. Richard Methot at the NOAA, NWFSC [@methot_stock_2013]. This most recent version was used because it included improvements and corrections to older model versions. The R package [r4ss](https://github.com/r4ss/r4ss), version 1.38.0, along with R version 4.0.1 were used to investigate and plot model fits. 


### Priors

```{r, echo=FALSE, results='asis'}
general_wd = "C:/Assessments/2021/copper_rockfish_2021/write_up/general_text"
filein = file.path(general_wd,'model_priors.Rmd')
read_child(filein)
```  

### Data Weighting

Length composition data for the commercial fishery started with a sample size determined from the equation listed in Sections \ref{commercial-fishery}. The input sample size for the recreational fishery length composition data was set equal to the number of length samples by year.   

The base  model weight length data for each fleet using the "Francis method" which was based on equation TA1.8 in Francis [-@francis_data_2011]. This formulation looks at the mean length or age and the variance of the mean to determine if across years, the variability is explained by the model. If the variability around the mean does not encompass the model predictions, then that data source should be down-weighted. This method accounts for correlation in the data (i.e., the multinomial distribution). Sensitivities were performed examining the difference in weighting using McAllister-Ianelli Harmonic Mean Weighting [@mcallister_bayesian_1997] and the Dirichlet-Multinomial Weighting [@thorson_model-based_2017].

### Estimated and Fixed Parameters

There were 123 estimated parameters in the base model. These included one parameter for $R_0$, 5 parameters for selectivity and time blocking of the fleets, 105 recruitment deviations, and 12 forecast recruitment deviations (Table \ref{tab:params}).

Fixed parameters in the model were as follows. Steepness was fixed at `r round(model$parameters[model$parameters$Label == "SR_BH_steep","Value"],2)`. Natural mortality was fixed at `r round(model$parameters[model$parameters$Label == "NatM_p_1_Fem_GP_1","Value"],3)` yr^-1^, the median of the prior, for both sexes .  The standard deviation of recruitment deviates was fixed at `r round(model$parameters[model$parameters$Label == "SR_sigmaR","Value"],2)`. Growth, maturity-at-length, and length-at-weight was fixed as described above in Section \ref{data}. 

Dome-shaped selectivity was explored for all fleets within the model. Older `r spp` are often found in deeper waters and may move into areas that limit their availability to fishing gear. After explorations, there was little support for dome-shaped selectivity for either fleet and the final selectivity form was fixed to be asymptotic. 


## Model Selection and Evaluation

The base assessment model for `r spp` was developed to balance parsimony and realism, and the goal was to estimate a spawning output trajectory for the population of `r spp` off the California coast north of Point Conception. The model contains many assumptions to achieve parsimony and uses many different sources of data to estimate reality. A series of investigative model runs were done to achieve the final base model.
