# Assessment Model

## Summary of Previous Assessments 

```{r, echo=FALSE, results='asis'}
general_wd = "C:/Assessments/2021/copper_rockfish_2021/write_up/general_text"
filein = file.path(general_wd,'model_previous_assess.Rmd')
read_child(filein)
```

### Bridging Analysis

```{r, echo=FALSE, results='asis'}
general_wd = "C:/Assessments/2021/copper_rockfish_2021/write_up/general_text"
filein = file.path(general_wd,'model_bridge.Rmd')
read_child(filein)
```


## Model Structure and Assumptions

`r Spp` north of Point Conception off the coast of California are assessed using a two-sex model with sex specific life history parameters.  The model assumed two fleets: 1) commercial and 2) recreational with removals beginning in `r startyr`. Selectivity was specified using the double normal parameterization within Stock Synthesis for both the commercial and recreational fleets. The commercial selectivity applied two time blocks for selectivity: `r startyr` - 2008 and 2009 - `r endyr`. The commercial selectivity block from `r startyr` - 2008  was fixed to be asymptotic, while the selectivity block from  2009 - `r endyr`was allowed to be dome-shaped.   The recreational fleet selectivity was constant across the model years, `r startyr` - `r endyr`, and fixed to be asymptotic, although dome-shape selectivity was explored during model development. Annual recruitment deviations were estimated for all years. 

### Modeling Platform and Structure

The assessment was conducted used Stock Synthesis version 3.30.16 developed by Dr. Richard Methot at the NOAA, NWFSC [@methot_stock_2013]. This most recent version was used because it included improvements and corrections to older model versions. The R package [r4ss](https://github.com/r4ss/r4ss), version 1.38.0, along with R version 4.0.1 were used to investigate and plot model fits. 


### Priors

```{r, echo=FALSE, results='asis'}
general_wd = "C:/Assessments/2021/copper_rockfish_2021/write_up/general_text"
filein = file.path(general_wd,'model_priors.Rmd')
read_child(filein)
```  

### Data Weighting

Length composition data for the commercial fishery started with a sample size determined from the equation listed in Sections \ref{commercial-fishery}. The input sample size for the recreational fishery length composition data was set equal to the number of length samples by year.   

The base  model weighted length data for each fleet using the "Francis method" which was based on equation TA1.8 in Francis [-@francis_data_2011]. This formulation looks at the mean length or age and its associated  standard error, and determines if, across years,  the model is able to adequately match the data. If the model predictions do not adequately match the mean lengths given the associated standard errors, then that data source should be down-weighted (equivalently, the standard errors are increased).  This method accounts for correlation in the data (i.e., the multinomial distribution). Sensitivities were performed examining the difference in weighting and model results using McAllister-Ianelli Harmonic Mean Weighting [@mcallister_bayesian_1997] and the Dirichlet-Multinomial Weighting [@thorson_model-based_2017].

### Estimated and Fixed Parameters

There were 123 estimated parameters in the base model. These included one parameter for $R_0$, 5 parameters for selectivity and time blocking of the fleets, 105 recruitment deviations, and 12 forecast recruitment deviations (Table \ref{tab:params}).

Fixed parameters in the model were as follows. Steepness was fixed at `r round(model$parameters[model$parameters$Label == "SR_BH_steep","Value"],2)`. Natural mortality was fixed at `r round(model$parameters[model$parameters$Label == "NatM_p_1_Fem_GP_1","Value"],3)` yr^-1^, the median of the prior, for both sexes .  The standard deviation of recruitment deviates was fixed at `r round(model$parameters[model$parameters$Label == "SR_sigmaR","Value"],2)`. Growth, maturity-at-length, and length-at-weight was fixed as described above in Section \ref{bio-data}. 

Dome-shaped selectivity was explored for all fleets within the model. Older `r spp` are often found in deeper waters and may move into areas that limit their availability to fishing gear. After explorations, there was little support for dome-shaped selectivity the recreational fleet and the final selectivity form was fixed to be asymptotic. Selectivity for the recreational fleet was estimated using the double normal parameterization where the ascending width and the size at peak selectivity were estimated.

For the commercial fleet in order to fit a shift in observed lengths, two blocks of selectivity were estimated: `r startyr` - 2008  and 2009 - `r endyr`.  Selectivity in each time block was estimated using the double normal parameterization where selectivity was assumed asymptotic from `r startyr` - 2008, estimating the ascending width and the size at peak selectivity, with the shape of selectivity estimated to be dome-shaped from 2009 - `r endyr`, estimating also the final selectivity parameter.


## Model Selection and Evaluation

The base assessment model for `r spp` was developed to balance parsimony and realism, with the goal of estimating a spawning output trajectory for the population of `r spp` off the California coast north of Point Conception. The model contains many assumptions to achieve parsimony and uses many different sources of data to estimate reality. A series of investigative model runs were developed to achieve the final base model.
