## Biological Data{#bio-data}

### Natural Mortality

```{r, echo=FALSE, results='asis'}
filein = file.path(general_wd,'data_m.Rmd')
read_child(filein)
```

### Length-Weight Relationship

```{r, echo=FALSE, results='asis'}
filein = file.path(general_wd,'data_length_weight.Rmd')
read_child(filein)
```

### Growth (Length-at-Age)

The length-at-age was estimated for male and female `r spp` south of Point Conception using data combined across multiple sources.  Given variable oceangraphic conditions north and south of Point Conception, among other factors, differences in growth patterns in the same species among areas may occur. Ideally a full area-specific growth curve would be externally estimated by sex (parameters $k$, $L_{\infty}$, $L1$, and $L2$ within Stock Synthesis) based on a single age and growth study. However, given limitations in ageing capacity  a targeted sampling approach was applied. The Cooperative Ageing Program (CAP) selected a subsample of larger (greater than 35 cm) of `r spp` observed by both the `r hkl` and the \Gls{s-wcgbt} (Figure \ref{fig:survey-len-at-age-data}). These observations were combined with simulated data based on a published growth study for `r spp` by Lea et al. [-@lea_biological_1999]. Fishes sampled by Lea et al. [-@lea_biological_1999] study were for the most part collected off central California between July 1978 through December 1985. This study included numerous observations of young fish and also reported the mean length, the number of observations, and the standard deviation of the length observations by age. These pieces of information were used to simulate length-at-age data that would be representative of the study's data for fish less than 5 years of age (since data on individual fish were not reported). The simulated data for young fish appeared consistent with data from older fish observed in the survey data sources (Figure \ref{fig:south-len-at-age-data}). This combined data set was used to calculate the growth curves for male and female `r spp` that were used in this assessment. The length-at-age observations from the surveys show minimal differences to those collected off the Oregon and Washington coast from fishery-dependent sources (Figure \ref{fig:len-at-age-comp}).

The calculated growth parameters used in this assessment indicated females and males have similar, if not identical, growth trajectories.  Sex-specific growth parameters were estimated at the following values:

\begin{centering}

Females $L_{\infty}$ = `r round(model$MGparmAdj$L_at_Amax_Fem_GP_1[1], 1)` cm; $k$ = `r round(model$MGparmAdj$VonBert_K_Fem_GP_1[1], 3)`

Males $L_{\infty}$ = `r round(model$MGparmAdj$L_at_Amax_Mal_GP_1[1], 1)` cm; $k$ = `r round(model$MGparmAdj$VonBert_K_Mal_GP_1[1], 3)`

\end{centering}

\vspace{0.75cm}

These values were fixed within the base model for male and female `r spp`. The coefficient of variation (CV) around young and old fish was fixed at a value of 0.10 for both sexes. The length-at-age curve with the CV around length-at-age by sex is shown in Figure \ref{fig:len-age-ss}. 

In contrast, the length-at-age values cited in the 2013 data-moderate assessment [@cope_data-moderate_2013] for `r spp` (although not directly used by the data-moderate model) were from Lea et al. [-@lea_biological_1999]. The $L_{\infty}$ from Lea et al. [-@lea_biological_1999] by sex were quite a bit larger than those estimated for this assessment. In Lea et al. [-@lea_biological_1999], young fish were well sampled; however, there were less than 5 observations of fish older than 12 years of age which appears to have led to a poorly informed estimate of $L_{\infty}$.    


### Maturation and Fecundity

Maturity-at-length was based on maturity reads conducted by Melissa Head at the NWFSC examining a total of 111 samples collected south of Point Conception by the `r hkl` and \Gls{s-wcgbt}. The maturity-at-length curve is based on an estimate of functional maturity rather than biological maturity. Biological maturity can include multiple behaviors that functional will exclude (e.g., abortive maturation and skip spawning). Biological maturity indicates that some energy reserves were used to create vitellogenin, but it does not mean that eggs will continue to develop and successfully spawn. This includes juvenile abortive maturation. Female rockfish commonly go through the first stages of spawning the year before they reach actual spawning capability. This is most likely a factor related to their complicated reproductive process of releasing live young. A subset of oocytes will develop early yolk, and then get aborted during the spawning season. Biological maturity also does not account for the proportion of oocytes in atresia (cellular breakdown and reabsorption), which means that fish that were skipping spawning for the season could be listed as biologically mature and functionally immature (Melissa Head, personal communication, NWFSC, NOAA). 

The 50 percent size-at-maturity was estimated at `r round(model$MGparmAdj[,"Mat50%_Fem_GP_1"][1], 1)` cm and slope of `r round(model$MGparmAdj$Mat_slope_Fem_GP_1[1], 2)` (Figure \ref{fig:maturity}). This area specific maturity-at-length estimate is relatively similar to the biological maturity curve assumed for `r spp` north of Point Conception based on the work of Hannah [-@hannah_length_2014] which estimated the 50 percent size-at-maturity of 34.8 cm and slope of -0.60.  

The fecundity-at-length was based on research from Dick et al. [-@dick_meta-analysis_2017]. The fecundity relationship for `r spp` was estimated equal to `r format(model$MGparmAdj$Eggs_scalar_Fem[1], scientific = TRUE)`$L$^`r round(model$MGparmAdj$Eggs_exp_len_Fem[1],2)`^ in millions of eggs where $L$ is length in cm. Fecundity-at-length is shown in Figure \ref{fig:fecundity}.


### Sex Ratio

```{r, echo=FALSE, results='asis'}
filein = file.path(general_wd,'data_sex_ratio.Rmd')
read_child(filein)
```