## Biological Data

### Natural Mortality

```{r, echo=FALSE, results='asis'}
filein = file.path(general_wd,'data_m.Rmd')
read_child(filein)
```

### Length-Weight Relationship

```{r, echo=FALSE, results='asis'}
filein = file.path(general_wd,'data_length_weight.Rmd')
read_child(filein)
```

### Growth (Length-at-Age)

The length-at-age was estimated for male and female `r spp` south of Point Conception using data combined across multiple sources.  Variable oceangraphic conditions north and south of Point Conception, differences in growth patterns in the same species among areas may occur. Ideally a full area specific growth curve would be estimated for both sexes ($k$, $L_{\infty}$, $L1$, and $L2$ within SS) would be estimated based on a single age and growth study, however, given limitation in ageing capacity developing a targeted approach was applied. The Cooperative Ageing Program (CAP) selected a subsample of larger (greater then 35 cm) of `r spp` observed by both the `r hkl` and the \Gls{s-wcgbt} survey (Figure \ref{fig:survey-len-at-age-data}). These observations were combined with simulated data based on a growth study from the south of Point Conception area.  A published growth study for `r spp` by Lea [-@lea_biological_1999] had numerous observations of young fish and also reported the mean length, the number of observations, and the standard deviation of the length observations by age. These pieces of information were used to simulate length-at-age data that would be representative of the study's data for fish less than 5 years of age. The simulated data for young fish appeared consistent with older fish observed in the survey data sources (Figure \ref{fig:south-len-at-age-data}). This combined data set was used to estimate growth curves for male and female `r spp` that were used in this assessment. The length-at-age observations from the survey collected fish shown minimal differences to those collected off the Oregon and Washington coast from fishery-dependent sources (Figure \ref{fig:len-at-age-comp}).

The estimated growth used in this assessment had female and males with similar growth.  Sex-specific growth parameters were estimated at the following values:

\begin{centering}

Females $L_{\infty}$ = `r round(model$MGparmAdj$L_at_Amax_Fem_GP_1[1], 1)` cm; $k$ = `r round(model$MGparmAdj$VonBert_K_Fem_GP_1[1], 3)`

Males $L_{\infty}$ = `r round(model$MGparmAdj$L_at_Amax_Mal_GP_1[1], 1)` cm; $k$ = `r round(model$MGparmAdj$VonBert_K_Mal_GP_1[1], 3)`

\end{centering}

These values were fixed within the base model for male and female `r spp`. While the growth differences between sexes was limited for `r spp`, sex-specific parameterization was selected in the anticipation of growth differences that were not observed. The coefficient of variation (CV) around young and old fish was fixed at a value of 0.10 for both sexes. The length-at-age curve with the CV around length-at-age by sex is shown in Figure \ref{fig:len-age-ss}. 

In contrast, the length-at-age values cited in the 2013 data-moderate assessment [@cope_data-moderate_2013] for `r spp` (although not directly used by the data-moderate model) were from Lea [-@lea_biological_1999]. The $L_{\infty}$ from the Lea study were quite a bit larger for both sexes than those estimated for this assessment. In the Lea [-@lea_biological_1999] young fish were well sampled, however, there were very few observations of fish older than 12 years of age (less than 5 total) which appears to have led to a poorly informed estimate of $L_{\infty}$.    


### Maturation and Fecundity

Maturity-at-length was based on maturity reads conducted by Melissa Head at the NWFSC examining a total of 111 samples collect south of Point Conception by the `r hkl` and \Gls{s-wcgbt} surveys. The maturity-at-length curve is based on an estimate of functional maturity rather than biological maturity. Biological maturity can include multiple behaviors that Functional will exclude (i.e., abortive maturation and skip spawning). Biological maturity indicates that some energy reserves were used to create vitellogenin, but it does not mean that eggs will continue to develop and successfully spawn. This includes juvenile abortive maturation. Rockfish commonly do a dummy run the year before they reach actual spawning capability. This is most likely a factor related to their complicated reproductive process of releasing live young.. A subset of oocyte will develop early yolk, and then get aborted during the spawning season. Biological maturity also does not account for the proportion of oocytes in atresia (cellular breakdown and reabsorption), which means that fish that were skipping spawning for the season could be listed as biologically mature and functionally immature (Melissa Head, personal communication, NWFSC, NOAA). 

The 50 percent size-at-maturity was estimated at `r round(model$MGparmAdj[,"Mat50%_Fem_GP_1"][1], 1)` cm and slope of `r round(model$MGparmAdj$Mat_slope_Fem_GP_1[1], 2)` with maturity asymptoting to 1.0 for larger fish (Figure \ref{fig:maturity}). This area specific maturity-at-length estimate is relatively similar to the the biological maturity curve assumed for `r spp` north of Point Conception based on the work of Hannah [-@hannah_length_2014] which estimated the 50 percent size-at-maturity of 34.8 cm and slope of -0.60.  

The fecundity-at-length was based on research Dick et al. [-@dick_meta-analysis_2017]. The fecundity relationship for `r spp` was estimated equal to `r format(model$MGparmAdj$Eggs_scalar_Fem[1], scientific = TRUE)`$L$^`r round(model$MGparmAdj$Eggs_exp_len_Fem[1],2)`^ in millions of eggs where $L$ is length in cm. Fecundity-at-length is shown in Figure \ref{fig:fecundity}.


### Sex Ratio

```{r, echo=FALSE, results='asis'}
filein = file.path(general_wd,'data_sex_ratio.Rmd')
read_child(filein)
```