## Biological Data

### Natural Mortality

```{r, echo=FALSE, results='asis'}
filein = file.path(general_wd,'data_m.Rmd')
read_child(filein)
```

### Length-Weight Relationship

```{r, echo=FALSE, results='asis'}
filein = file.path(general_wd,'data_length_weight.Rmd')
read_child(filein)
```

### Growth (Length-at-Age)

The length-at-age was estimated for male and female `r spp` using a mixture of data collected from fishery-dependent data sources off the coast of Oregon and Washington that were collected from 1998-2019 (Table \ref{tab:len-at-age-samps} and Figure \ref{fig:len-age-data}) and length-at-age data from larger `r spp` captured by the `r hkl` and the \Gls{s-wcgbt} surveys. Given variable oceangraphic conditions north and south of Pt. Conception{, it is relatively common to observe variations of growth in the same species by area.  Ideally a full area specific growth curve would be estimated for both sexes ($k$, $L_{\infty}$, $L1$, and $L2$ within SS), however, given limitation in ageing capacity developing an area specific $L_{\infty}$ was prioritized. The Cooperative Ageing Program (CAP) selected a subsample of larger (greater then 35 cm) of `r spp` observed by both surveys. The resulting length-at-age curve used smaller fish sampled off the coast of Oregon and Washington to estimate $k$ and $L1$ parameters and the age-length data from the `r hkl` and \Gls{s-wcgbt} surveys to estimate sex specific $L_{\infty}$ parameters.

ADD FIGURE SHOWING LENGTHS-AT-AGE

Figure \ref{fig:len-age} shows the lengths and ages for all years by data source as well as predicted von Bertalanffy fits to the data. Females grow larger than males and sex-specific growth parameters were estimated at the following values:

\begin{centering}

Females $L_{\infty}$ = `r round(model$MGparmAdj$L_at_Amax_Fem_GP_1[1], 1)` cm; $k$ = `r round(model$MGparmAdj$VonBert_K_Fem_GP_1[1], 3)`

Males $L_{\infty}$ = `r round(model$MGparmAdj$L_at_Amax_Mal_GP_1[1], 1)` cm; $k$ = `r round(model$MGparmAdj$VonBert_K_Mal_GP_1[1], 3)`

\end{centering}

These values were fixed within the base model for male and female `r spp`. The coefficient of variation (CV) around young and old fish was fixed at a value of 0.10. The length-at-age curve with the CV around length-at-age by sex is shown in Figure \ref{fig:len-age-ss}.

In contrast, the length-at-age values cited in the 2013 data-moderate assessment [@cope_data-moderate_2013] for `r spp` (although not directly used by XDB-SRA), were from Lea [-@lea_biological_1999]. The $L_{\infty}$ from the Lea study were quite a bit larger for both sexes than those estimated for this assessment using recent length and age data off the coast of Oregon and Washington. However, the data presented in Lea [-@lea_biological_1999] reflected fish sampled off the coast of California and showed very few fish sampled that were greater than 12 years of age.   


### Maturation and Fecundity

Maturity-at-length was based on maturity reads conducted by Melissa Head at the NWFSC examining a total of 111 samples collect South of Pt. Conception by the `r hkl` and \Gls{s-wcgbt} surveys. The maturity-at-length curve is based on an estimate of functional maturity rather than biological maturity. Biological maturity can include multiple behaviors that Functional will exclude (i.e., abortive maturation and skip spawning). Biological maturity indicates that some energy reserves were used to create vitellogenin, but it does not mean that eggs will continue to develop and successfully spawn. This includes juvenile abortive maturation. Rockfish commonly do a dummy run the year before they reach actual spawning capability. This is most likely a factor related to their complicated reproductive process of releasing live young.. A subset of oocyte will develop early yolk, and then get aborted during the spawning season. Biological maturity also does not account for the proportion of oocytes in atresia (cellular breakdown and reabsorption), which means that fish that were skipping spawning for the season could be listed as biologically mature and functionally immature (Melissa Head, personal communication, NWFSC, NOAA). 

The 50% size-at-maturity was estimated at `r round(model$MGparmAdj[,"Mat50%_Fem_GP_1"][1], 1)` cm and slope of `r round(model$MGparmAdj$Mat_slope_Fem_GP_1[1], 2)` with maturity asymptoting to 1.0 for larger fish (Figure \ref{fig:maturity}). This area specific maturity-at-length estimate is relatively similar to the the biological maturity curve assumed for `r spp` North of Pt. Conception based on the work of Hannah [-@hannah_length_2014] which estimated the 50% size-at-maturity of 34.8 cm and slope of -0.60.  

The fecundity-at-length was based on research Dick et al. [-@dick_meta-analysis_2017]. The fecundity relationship for `r spp` was estimated equal to `r format(model$MGparmAdj$Eggs_scalar_Fem[1], scientific = TRUE)`$L$^`r round(model$MGparmAdj$Eggs_exp_len_Fem[1],2)`^ in millions of eggs where $L$ is length in cm. Fecundity-at-length is shown in Figure \ref{fig:fecundity}.




### Sex Ratio

```{r, echo=FALSE, results='asis'}
filein = file.path(general_wd,'data_sex_ratio.Rmd')
read_child(filein)
```