\clearpage
# Tables

<!-- ======================================================= -->
<!-- ***************    Catches      *********************** --> 
<!-- ======================================================= -->

\include{tex_tables/Catches_All_Years.tex}

\newpage


```{r, results = 'asis'}
yrs = hist = 2011:2020
nfleets = 2
catch = dead = total.dead = 0
for (i in 1:nfleets){
  name = paste0("retain(B):_",i)
  input.catch = model$timeseries[model$timeseries$Yr %in% yrs, name]
  catch = cbind(catch, input.catch)
}
total.catch <- round(apply(catch, 1, sum),2)

man = read.csv("//nwcfile/FRAM/Assessments/CurrentAssessments/DataModerate_2021/copper_rockfish/management/copper_south.csv")
man = man[man$Year %in% yrs, ]
out = cbind(man, total.catch)

col_names = c("Year", "OFL", "ACL", "Total Removals")

table_format(x = out,
             caption = "The OFL and ACL for south of 40.10 Latitude N. and the total removals south of Point Conception.",
             label = "ofl",
             align = 'l',
             col_names = col_names)
```


<!-- ======================================================= -->
<!-- *************** Com. Catch Ratio  ********************* --> 
<!-- ======================================================= -->

\include{tex_tables/historical_landings_tables_2020_revised_Avila_1953.tex}

\newpage

<!-- ======================================================= -->
<!-- ***************       Data      *********************** --> 
<!-- ======================================================= -->

\include{tex_tables/CA_S_Samples.tex}

\newpage


\include{tex_tables/s_ca_rec_len_samples_mar2021.tex}

\newpage

\include{tex_tables/sca_hkl_length_SampleSize.tex}

\newpage

\include{tex_tables/hkl_index_for_doc.tex}

\newpage

\include{tex_tables/south_length_SampleSize.tex}

\newpage

<!-- ======================================================= -->
<!-- ***************    Biology      *********************** --> 
<!-- ======================================================= -->

```{r, echo=FALSE, results='asis'}
filein = file.path(general_wd,'table_growth.Rmd')
read_child(filein)
```
\newpage

<!-- ======================================================= -->
<!-- ***********   Model Parameters     ******************** --> 
<!-- ======================================================= -->


```{r, results = 'asis'}
mod_params = model$parameters[-c(grep('Impl',model$parameters$Label),
							     grep('Fore',model$parameters$Label)),
                                (names(model$parameters) %in%
                                c("Num","Label","Value","Phase","Min",
                                  "Max","Status","Parm_StDev",
                                  "Pr_type","Prior","Pr_SD"))] 
mod_params[,'Value'] = round(as.numeric(mod_params[,'Value']),3)                                 
# Combine bounds into one column
mod_params$Min = paste('(', mod_params$Min, ', ', mod_params$Max, ')', sep='')
# Combine prior info to one column
mod_params$PR_type = ifelse(mod_params$Pr_type == 'No_prior' , 'None', paste(mod_params$Pr_type,' (', mod_params$Prior,  ', ', mod_params$Pr_SD, ')', sep = ''))
# Set long value to scientific notation
mod_params[mod_params$Label == "Wtlen_1_Fem",3] = format(mod_params[mod_params$Label == "Wtlen_1_Fem",3], scientific = TRUE)
mod_params[mod_params$Label == "Wtlen_1_Mal",3] = format(as.numeric(mod_params[mod_params$Label == "Wtlen_1_Mal",3]), scientific = TRUE)
mod_params[mod_params$Label == "Eggs_scalar_Fem",3] = format(as.numeric(mod_params[mod_params$Label == "Eggs_scalar_Fem",3]), scientific = TRUE)
mod_params[mod_params$Label == "L_at_Amax_Mal_GP_1",3] = round(as.numeric(mod_params[mod_params$Label == "L_at_Amax_Mal_GP_1",3]), 4)
mod_params[mod_params$Label == "VonBert_K_Mal_GP_1",3] = round(as.numeric(mod_params[mod_params$Label == "VonBert_K_Mal_GP_1",3]), 3)
mod_params[mod_params$Label == "CV_old_Mal_GP_1",3] = round(as.numeric(mod_params[mod_params$Label == "CV_old_Mal_GP_1",3]), 3)
# Remove the max, prior and prior sd columns
drops = c('Max', 'Prior', 'Pr_type', 'Pr_SD', 'Num')
mod_params = mod_params[, !(names(mod_params) %in% drops)]
rownames(mod_params) = c()
mod_params[,"Label"] = gsub("\\_", " ", mod_params[,"Label"])
mod_params[,"PR_type"] = gsub("\\_", " ", mod_params[,"PR_type"])
# Add column names
col_names = c('Parameter',
                         'Value',
                         'Phase',
                         'Bounds',
                         'Status',
                         'SD',
                         'Prior (Exp.Val, SD)')
table_format(x = mod_params,
             caption = "List of parameters used in the base model, including estimated values and standard deviations (SD), bounds (minimum and maximum), estimation phase (negative values not estimated), status (indicates if parameters are near bounds), and prior type information (mean and SD).",
             label = "params",
             align = 'l',
             col_names = col_names,
             longtable = TRUE,
             font_size = 9,
             landscape = TRUE,
             custom_width = TRUE,
             col_to_adjust = c(1,7), 
             width = c("6cm", "4cm"))                         
```

<!-- ======================================================= -->
<!-- ***********    Like Contributions  ******************** --> 
<!-- ======================================================= -->

\include{tex_tables/likelihoods.tex}


<!-- ======================================================= -->
<!-- ***********       Time Series      ******************** --> 
<!-- ======================================================= -->

\include{tex_tables/TimeSeries.tex}

\newpage

<!-- ======================================================= -->
<!-- ****************     Sensitivities      *************** --> 
<!-- ======================================================= -->


\newpage

```{r, results = 'asis'}
tab = read.csv(file.path(mod_loc, 'tables', 'data_weights.csv'))
col_names = c('Method',
			  'Commercial Lengths',
              'Recreational Lengths',
			  'NWFSC Hook and Line')
table_format(x = tab,
             caption = "Data weights applied by each alternative data weighting methods.",
             label = "dw",
             align = 'l',
             col_names = col_names)
```

\newpage

\include{tex_tables/sensitivities_1.tex}

\newpage

\include{tex_tables/sensitivities_2.tex}

\newpage

<!-- ======================================================= -->
<!-- ********  Reference Points & Management *************** --> 
<!-- ======================================================= -->

\include{tex_tables/e_ReferencePoints_ES.tex}

\newpage


```{r, results = 'asis'}
tab = read.csv(file.path(mod_loc, 'tables', 'g_Projections_ES.csv'))

man_south = read.csv("//nwcfile/FRAM/Assessments/CurrentAssessments/DataModerate_2021/copper_rockfish/management/copper_south.csv")

ofl_s = man_south[man_south$Year %in% c(2021, 2020), "OFL"] 
acl_s = man_south[man_south$Year %in% c(2021, 2022), "ACL"]

find = which(model$timeseries$Yr %in% c(2021, 2022))
rm = model$timeseries[find, "dead(B):_1"] + model$timeseries[find, "dead(B):_2"]

out = cbind(tab$Year,
            c(ofl_s, rep("-",10)),
            c(acl_s, rep("-",10)),
            c(rm, rep("-",10)),
            c(rep("-",2), round(tab[3:12,2], 2)),
            c(rep("-",2), round(tab[3:12,3],2)),
            c(rep("-",2), round(tab[3:12,3]/tab[3:12,2], 3)),
            round(tab[ ,5:ncol(tab)], 2))

col_names = c('Year',
              'S. 40.10 OFL',
              'S. 40.10 ACL',
              "Assumed Removals",
              "OFL", 
              "ABC", 
              "Buffer",
              "Spawning Output",
              "Fraction Unfished")

table_format(x = out,
             caption = "Projections of potential OFLs (mt), ACLs (mt), the assumed removals based on 2021 and 2022 adopted ACL values, estimated spawning output, and fraction unfished. The OFL and ACL for 2021 and 2022 reflect adopted management limits for the area south of 40.10 Latitude N.",
             label = "project",
             landscape = TRUE,
             align = 'l',
             custom_width = TRUE,
             col_to_adjust = c(2,3,4,5,6,7,8,9), 
             width = c("3cm", "3cm","3cm","3cm","3cm","3cm","3cm","3cm"),
             col_names = col_names)

```

\newpage