\clearpage
# Tables

<!-- ======================================================= -->
<!-- ***************    Catches      *********************** --> 
<!-- ======================================================= -->

\include{tex_tables/Catches_All_Years.tex}

\newpage


```{r, results = 'asis'}
yrs = hist = 2011:2020
nfleets = 2
catch = dead = total.dead = 0
for (i in 1:nfleets){
  name = paste0("retain(B):_",i)
  input.catch = model$timeseries[model$timeseries$Yr %in% yrs, name]
  catch = cbind(catch, input.catch)
}
total.catch <- round(apply(catch, 1, sum),2)


north = read.csv("//nwcfile/FRAM/Assessments/CurrentAssessments/DataModerate_2021/copper_rockfish/management/copper_north.csv")

south = read.csv("//nwcfile/FRAM/Assessments/CurrentAssessments/DataModerate_2021/copper_rockfish/management/copper_south.csv")


south = round(south,2)
south[is.na(south)] = "-"
north = round(north,2)
north[is.na(north)] = "-"

north = north[north$Year %in% yrs, ]
south = south[south$Year %in% yrs, ]
out = cbind(south, north[,2:3], round(north$OFL, 2), round(north$ACL * 0.25, 2), 
            round(south$ACL + 0.25*north$ACL,2), total.catch)

col_names = c("Year", 
              "Complex OFL - S.",
              "Complex ACL - S.",
              "OFL - S. ", 
              "ACL - S.", 
              "Complex OFL - N.",
              "Complex ACL - N.",              
              "OFL - N.",  
              "CA ACL - N.", 
              "CA ACL Total", 
              "N. CA Removals")

table_format(x = out,
             caption = "The complex level OFL (mt) and ACL (mt) for Nearshore Rockfish north and south of 40.10 Latitude N., the copper rockfish OFL (mt) and ACL (mt) contributions, the total ACL allocated to California, and the total removals (mt) from south of Point Conception.",
             label = "ofl",
             align = 'l',
             landscape = TRUE,
             custom_width = TRUE,
             col_to_adjust = 2:ncol(out), 
             width = rep("1.5cm", ncol(out)),
             col_names = col_names)
```


<!-- ======================================================= -->
<!-- *************** Management Reg.   ********************* --> 
<!-- ======================================================= -->


<!-- ======================================================= -->
<!-- *************** Com. Catch Ratio  ********************* --> 
<!-- ======================================================= -->

\include{tex_tables/historical_landings_tables_2020_revised_Avila_1953.tex}

\newpage

<!-- ======================================================= -->
<!-- ***************       Data      *********************** --> 
<!-- ======================================================= -->

\include{tex_tables/CA_S_Samples.tex}

\newpage


\include{tex_tables/s_ca_rec_len_samples_may2021.tex}

\newpage

\include{tex_tables/sca_hkl_length_SampleSize.tex}

\newpage

\include{tex_tables/hkl_index.tex}

\newpage

\include{tex_tables/south_length_SampleSize.tex}

\newpage


<!-- ======================================================= -->
<!-- ***************    Biology      *********************** --> 
<!-- ======================================================= -->

```{r, echo=FALSE, results='asis'}
filein = file.path(general_wd,'table_growth.Rmd')
read_child(filein)
```
\newpage

<!-- ======================================================= -->
<!-- ***********   Model Parameters     ******************** --> 
<!-- ======================================================= -->


```{r, results = 'asis'}
mod_params = model$parameters[-c(grep('Impl',model$parameters$Label),
                   grep('Fore',model$parameters$Label)),
                                (names(model$parameters) %in%
                                c("Num","Label","Value","Phase","Min",
                                  "Max","Status","Parm_StDev",
                                  "Pr_type","Prior","Pr_SD"))] 
mod_params[,'Value'] = round(as.numeric(mod_params[,'Value']),3)                                 
# Combine bounds into one column
mod_params$Min = paste('(', mod_params$Min, ', ', mod_params$Max, ')', sep='')
# Combine prior info to one column
mod_params$PR_type = ifelse(mod_params$Pr_type == 'No_prior' , 'None', paste(mod_params$Pr_type,' (', mod_params$Prior,  ', ', mod_params$Pr_SD, ')', sep = ''))
# Set long value to scientific notation
mod_params[mod_params$Label == "Wtlen_1_Fem",3] = format(mod_params[mod_params$Label == "Wtlen_1_Fem",3], scientific = TRUE)
mod_params[mod_params$Label == "Wtlen_1_Mal",3] = format(as.numeric(mod_params[mod_params$Label == "Wtlen_1_Mal",3]), scientific = TRUE)
mod_params[mod_params$Label == "Eggs_scalar_Fem",3] = format(as.numeric(mod_params[mod_params$Label == "Eggs_scalar_Fem",3]), scientific = TRUE)
mod_params[mod_params$Label == "L_at_Amax_Mal_GP_1",3] = round(as.numeric(mod_params[mod_params$Label == "L_at_Amax_Mal_GP_1",3]), 4)
mod_params[mod_params$Label == "VonBert_K_Mal_GP_1",3] = round(as.numeric(mod_params[mod_params$Label == "VonBert_K_Mal_GP_1",3]), 3)
mod_params[mod_params$Label == "CV_old_Mal_GP_1",3] = round(as.numeric(mod_params[mod_params$Label == "CV_old_Mal_GP_1",3]), 3)
# Remove the max, prior and prior sd columns
drops = c('Max', 'Prior', 'Pr_type', 'Pr_SD', 'Num')
mod_params = mod_params[, !(names(mod_params) %in% drops)]
rownames(mod_params) = c()
mod_params[,"Label"] = gsub("\\_", " ", mod_params[,"Label"])
mod_params[,"PR_type"] = gsub("\\_", " ", mod_params[,"PR_type"])
# Add column names
col_names = c('Parameter',
                         'Value',
                         'Phase',
                         'Bounds',
                         'Status',
                         'SD',
                         'Prior (Exp.Val, SD)')
table_format(x = mod_params,
             caption = "List of parameters used in the base model, including estimated values and standard deviations (SD), bounds (minimum and maximum), estimation phase (negative values not estimated), status (indicates if parameters are near bounds), and prior type information (mean and SD).",
             label = "params",
             align = 'l',
             col_names = col_names,
             longtable = TRUE,
             font_size = 9,
             landscape = TRUE,
             custom_width = TRUE,
             col_to_adjust = c(1,7), 
             width = c("6cm", "4cm"))                         
```

<!-- ======================================================= -->
<!-- ***********    Like Contributions  ******************** --> 
<!-- ======================================================= -->

\include{tex_tables/likelihoods.tex}


<!-- ======================================================= -->
<!-- ***********       Time Series      ******************** --> 
<!-- ======================================================= -->

\include{tex_tables/TimeSeries.tex}

\newpage

<!-- ======================================================= -->
<!-- ****************     Sensitivities      *************** --> 
<!-- ======================================================= -->


\newpage

```{r, results = 'asis'}
tab = read.csv(file.path(mod_loc, 'tables', 'data_weights.csv'))
col_names = c('Method',
        'Commercial Lengths',
              'Recreational Lengths',
        'NWFSC Hook and Line')
table_format(x = tab,
             caption = "Data weights applied by each alternative data weighting method.",
             label = "dw",
             align = 'l',
             col_names = col_names)
```

\newpage


\include{tex_tables/sensitivities_1_final.tex}

\newpage

\include{tex_tables/sensitivities_2_final.tex}

\newpage


<!-- ======================================================= -->
<!-- ********  Reference Points & Management *************** --> 
<!-- ======================================================= -->

\include{tex_tables/e_ReferencePoints_ES.tex}

\newpage


```{r, results = 'asis'}
tab = read.csv(file.path(mod_loc, 'tables', 'g_Projections_ES.csv'))

man_south = read.csv("//nwcfile/FRAM/Assessments/CurrentAssessments/DataModerate_2021/copper_rockfish/management/copper_south.csv")

man_north = read.csv("//nwcfile/FRAM/Assessments/CurrentAssessments/DataModerate_2021/copper_rockfish/management/copper_north.csv")

com_ofl_s = round(man_south[man_south$Year %in% c(2021, 2020), "Complex.OFL"], 1) 
com_acl_s = round(man_south[man_south$Year %in% c(2021, 2022), "Complex.ACL"], 1)
ofl_s = round(man_south[man_south$Year %in% c(2021, 2020), "OFL"], 1) 
acl_s = round(man_south[man_south$Year %in% c(2021, 2022), "ACL"], 1)

com_ofl_n = round(man_north[man_north$Year %in% c(2021, 2020), "Complex.OFL"], 1) 
com_acl_n = round(man_north[man_north$Year %in% c(2021, 2022), "Complex.ACL"], 1)
ofl_n = round(man_north[man_north$Year %in% c(2021, 2020), "OFL"], 1) 
acl_n = round(0.25*man_north[man_north$Year %in% c(2021, 2022), "ACL"], 1)

sigma = c(1, 1*(1+(1:11-1)*0.075))
buffer = exp(stats::qnorm(0.45, 0, sigma))

find = which(model$timeseries$Yr %in% c(2021, 2022))
rm = model$timeseries[find, "dead(B):_1"] + model$timeseries[find, "dead(B):_2"]

out = cbind(tab$Year,
            c(ofl_s, rep("-",10)),
            c(acl_s, rep("-",10)),
            c(ofl_n, rep("-",10)),
            c(acl_n, rep("-",10)),
            c(acl_s + acl_n, rep("-", 10)),
            c(rm, rep("-",10)),
            c(rep("-",2), round(tab[3:12,2], 2)),
            c(rep("-",2), round(tab[3:12,2] * buffer[3:12], 2)),
            c(rep("-",2), round(buffer[3:12], 3)),
            c(rep("-",2), round(tab[3:12,3],2)),
            round(tab[ ,5:ncol(tab)], 2))

col_names = c('Year',
              'OFL - S. 40.10',
              'ACL - S. 40.10',
              'OFL - N. 40.10',
              'CA ACL - N. 40.10',
              'Total CA ACL',
              "Removals",
              "OFL",
              "ABC",
              "Buffer", 
              "ACL", 
              "Spawning Output",
              "Fraction Unfished")

table_format(x = out,
             caption = "Projections of potential OFLs (mt), ABCs (mt), the assumed removals based on 2021 and 2022 adopted ACL values, estimated spawning output, and fraction unfished. The OFLs and ACLs reflect adopted species-specific contribution for copper rockfish by area. The California (CA) ACL is the sum of the species-specific ACL for south of 40.10 N. Lat. and the percent of the species-specific ACL for north of 40.10 N. Lat. allocated to California.",
             label = "project",
             landscape = TRUE,
             align = 'l',
             font_size = 9.5,             
             custom_width = TRUE,
             col_to_adjust = 2:ncol(out), #c(2,3,4,5,6,7,8,9,10,11,12), 
             width = c("1.35cm","1.35cm","1.35cm","1.35cm","1.5cm","1.4cm","1.3cm","1.4cm","1.5cm","1.4cm"),
             col_names = col_names)

```

\clearpage

\input{tex_tables/decision_table.tex}

\clearpage


```{r, results = 'asis'}  

sca = r4ss::SS_output("C:/Assessments/2021/copper_rockfish_2021/models/ca_s_pt_c/12.1_base", printstats = FALSE, verbose = FALSE)
nca = r4ss::SS_output("C:/Assessments/2021/copper_rockfish_2021/models/ca_n_pt_c/10.3_base",
  printstats = FALSE, verbose = FALSE)

find <- sca[["timeseries"]][["Yr"]] <= (sca$endyr + 1)
ssb_south <- sca[["timeseries"]][["SpawnBio"]][find]

find <- nca[["timeseries"]][["Yr"]] <= (nca$endyr + 1)
ssb_north <- nca[["timeseries"]][["SpawnBio"]][find]

ssb_total <- ssb_south + ssb_north

out = data.frame(sca[["timeseries"]][["Yr"]][find], 
      round(ssb_north, 2), 
      round(ssb_south, 2), 
      round(ssb_total, 2), 
      round(ssb_north/ssb_north[1], 3),
      round(ssb_south/ssb_south[1], 3),
        round(ssb_total / ssb_total[1], 3))
colnames = c("Year", 
       "SO-North",
       "SO-South",
       "SO-CA",
       "Rel. SO-North",
       "Rel. SO-South",
       "Rel. SO-CA")

table_format(x = out,
             caption = "Spawning output (SO) south and north of Point Conception in California, total spawning output across California, relative spawning output (Rel. SO) north and south of Point Conception, and relative spawning output across California.",
             label = "ca-ssb-status",
             align = 'l',
             col_names = colnames)

```

\newpage