\clearpage

# Appendix

## Detailed Fit to Length Composition Data{#length-fit}


```{r, results='asis'}
plot_info = read.csv(file.path(mod_loc, "plots", "plotinfotable_for_doc.csv"))
len_fit = plot_info[which(plot_info$category == "LenComp"), ]
plot.vec = grep("comp_lenfit_flt", len_fit$label)
filein = file.path(mod_loc, "plots")
for (a in plot.vec){
	cap = len_fit$caption[a]
	lab = len_fit$label[a]
	add_figure(filein = file.path(filein, len_fit$file[a]), 
			   caption = cap, 
			   label = lab)
}
```

\newpage

## Annual Length Composition Data{#length-data} 

```{r, results='asis'}
plot_info = read.csv(file.path(mod_loc, "plots", "plotinfotable_for_doc.csv"))
len_fit = plot_info[which(plot_info$category == "CompDat"), ]
plot.vec = grep("comp_lendat_flt", len_fit$label)
filein = file.path(mod_loc, "plots")
for (a in plot.vec){
	cap = len_fit$caption[a]
	lab = len_fit$label[a]
	add_figure(filein = file.path(filein, len_fit$file[a]), 
			   caption = cap, 
			   label = lab)
}
```

\newpage

## Implied Fit to Commercial 'Ghost' Fleet Length Data 

The 'ghost' fleet data consist of commercial length samples collected prior to 1995 which were not used in the base model due to low sample sizes which resulted in noisy length distributions.  

```{r, results='asis'}
plot_info = read.csv(file.path(mod_loc, "plots", "plotinfotable_for_doc.csv"))
len_fit = plot_info[which(plot_info$category == "LenComp"), ]
plot.vec = grep("comp_gstlenfit_flt1mkt0", len_fit$label)
filein = file.path(mod_loc, "plots")
for (a in plot.vec){
	cap = len_fit$caption[a]
	lab = len_fit$label[a]
	add_figure(filein = file.path(filein, len_fit$file[a]), 
			   caption = cap, 
			   label = lab)
}
``` 

## Summary of California Management Measures{#ca-man}

Information on changes to California management measures across time can be found in the separate file "California Nearshore Regulation History-Data Moderate Accompanying Material.pdf".


## Percent of Habitat Area Closed to Fishing for Groundfish in the Rockfish Conservation Areas, Cowcod Conservation Areas, and Marine Protected Areas in California from 2001-2021{#ca-closed-open}

```{r, echo=FALSE, results='asis'}
filein = file.path(general_wd,'appendix_ca_open_closed.Rmd')
read_child(filein)
```

\newpage


## California Remotely Operated Vehicle Data 

From 2013-2015, the CDFW in collaboration with Marine Applied Research and Exploration (MARE), conducted Remote Operated Vehicle (ROV) surveys along the full length of the California coastline inside MPAs and in reference sites outside for comparison. Density estimates were produced from the ratio of observed fish per unit area observed over the area of seafloor observed by the ROV in fish per meter squared. The percent relative density reflecting the proportion of the density observed in each depth bin was estimated relative to the sum of the density values in observed depths. A particular advantage of ROV data compared to other data sources is the accuracy of the depth of encounter of individual fish, providing useful information regarding selectivity of fishing gear relative to the depth distribution of fish observed by the ROV. 
 
In addition, length frequency distributions by depth were determined from fish observed by the ROV based on visual approximations using the distance between paired lasers. While future efforts to increase the precision of length estimates include using stereo-camera data and programs estimating length from trigonometric calculations, the trends in approximate length distribution with depth still provides useful information. Length frequency distributions for `r spp` sampled by the ROV in reference locations open to fishing south of Point Conception show the majority of observations occurring between 10 - 20 fathoms with peak observations between 20 - 40 cm (Figure \ref{fig:rov-open}). The observations in closed areas, marine protected areas where retention is prohibited, had higher number of observations of `r spp` across sizes and depths (Figure \ref{fig:rov-mpa}). Smaller sizes were observed in higher proportions across depth in open areas (Figure \ref{fig:rov-percent-open}) versus closed areas (Figure \ref{fig:rov-percent-mpa}). 


```{r, results = 'asis'}
add_figure(
filein = file.path(data_loc, "survey", "rov",  "copper_socal_open_area.png"), 
caption = "Length frequency distribution in each 10 fm depth bin for copper rockfish sampled by the ROV in reference locations open to fishing south of Point Conception",
label = 'rov-open')
```

\clearpage

```{r, results = 'asis'}
add_figure(
filein = file.path(data_loc, "survey", "rov",  "copper_socal_mpa_area.png"), 
caption = "Length frequency distribution in each 10 fm depth bin for copper rockfish sampled by the ROV in marine protected areas where fishing for groundfish is prohibited",
label = 'rov-mpa')
```

\clearpage

```{r, results = 'asis'}
add_figure(
filein = file.path(data_loc, "survey", "rov",  "copper_socal_percent_open.png"), 
caption = "Percent composition of copper rockfish length frequency in 5 cm size classes for each 10 fm depth bin from ROV observations south of Point Conception in reference locations where fishing for groundfish is allowed",
#width = 150,
#height = 150,
label = 'rov-percent-open')
```

\clearpage

```{r, results = 'asis'}
add_figure(
filein = file.path(data_loc, "survey", "rov",  "copper_socal_percent_mpa.png"), 
caption = "Percent composition of copper rockfish length frequency in 5 cm size classes for each 10 fm depth bin from ROV observations south of Point Conception in marine protected areas where fishing for groundfish is prohibited",
#width = 150,
#height = 150,
label = 'rov-percent-mpa')
```

\clearpage

## Evaluating available information to determine stock management delineation for copper rockfish (_Sebastes caurinus_) off the U.S. West Coast{#man-area}

The following analysis examines the available literature that could inform the selection of management areas for stocks that are assessd at finer regional scales such as `r spp`. This analysis was presented at the  Groundfish Sub-committee of the Scientific and Statiscal Committee held on September 29, 2021. 

### Dispersal

#### Recruitment and Dispersal

_Evidence for Managing at Assessment Scale_

Markel [-@markel_rockfish_2011] - Observed significant differences of recruitment among sites and years which were not consistent, indicating spatial differences in recruitment intensity during year of high recruitment within the Barkley Sound, British Columbia. 

Buonaccorsi et al. [-@buonaccorsi_population_2002]: Estimated the dispersal distance of `r spp` recruits as 13km or less based on a stepping stone model. Caveat: This value can be highly sensitive to the ratio of total population size to effective population size. 

While annual recruitment deviations were not estimated in the base model for the area south of Point Conception, model sensitivities to estimating annual recruitment deviations appeared to be little coherence with strong or weak recruitment years between the models south and north of Point Conception. The base model for the area south of Point Conception opted to not estimate annual recruitment deviations due to correlations with recent high catch years (i.e., estimated a series of years [2008 - 2014] with high recruitment proceeding recent years with high catches between).  *Caveat*: length data may not be fully informative on recruitment and variation in growth can result in low or high recruitment years being attributed to multiple years. 


_Evidence for Alternative Management Scale_

Field et al. [-@field_spatiotemporal_2021] - Determined that rockfish strong recruitments observed between 2014-2016 were largely coastwide events.


<!---------------------------------------------------->

#### Adult Movement 

_Evidence for Managing at Assessment Scale_

Lea et al [-@lea_biological_1999]: Summarized tagging data that reported `r spp` to have low to moderate degrees of movement and high site fidelity. Of 32 tagged `r spp` that were recaptured the distance moved ranged between 0-1.5 nautical miles after 2-1,017 days at liberty. 

Reynolds et al. [@reynolds_application_2010]: Tagged `r spp` in nearshore waters of Prince William Sound, Alaska exhibited long periods of residency with limited movements. 

Tolimieri et al. [-@tolimieri_home_2009]: Observed home ranges of `r spp` in Puget Sound was relatively small (~1500 to ~2500m$^2$). Caveat: movement of `r spp` in the Puget Sound may not be representative of movement of coastal populations. 

_Evidence for Alternative Management Scale_

Lowe et al. [-@lowe_site_2009]: `r Spp` exhibited low degrees of site fidelity and had high variation in the percentage of days on which individuals were detected based on 7 tagged fish at petroleum platforms in the Santa Barbara Channel.

McGilliard et al. [-@mcgilliard_accounting_2015]: Fisheries managed by area closures impose spatial heterogeneity in fishing mortality, and simulations from generic operating models suggest that the accuracy of conventional stock assessments depends on movement rates.

<!---------------------------------------------------->

### Geographic variation

#### Variation in Genetic Composition 

_Evidence for Managing at Assessment Scale_

Sivasundar and Palumbi [-@sivasundar_life_2010]: Measured moderate differentiation mtDNA structure but no nuclear structure in coastal `r spp` populations. 

Buonaccorsi et al. [-@buonaccorsi_population_2002]: Identified significant divergence along the U.S. West Coast when measured as variance in allele frequency or mean repeat number, indicting a substantial isolation between regions. Examined samples from Queen Charlotte, Puget Sound, Canadian Gulf Islands, Crescent City, Big Creek, San Miguel Island.

Johansson et al. [-@johansson_influence_2008]: Identified isolation by distance in coastal `r spp` populations ($\text{F}_\text{ST}$ = 0.006) similar to Buonaccorsi et al. [-@buonaccorsi_population_2002]  ($\text{F}_\text{ST}$ = 0.008). However, concluded that some of the genetic divergence may be related to habitat patchiness and not distance alone.

_Evidence for Alternative Management Scale_

Sivasundar and Palumbi [-@sivasundar_life_2010]: The Oregon and Monterey Bay populations were both genetically differentiated from the Santa Barbara populations for mtDNA but the Monterey Bay and Oregon populations could not be distinguished from each other. This could indicate that there is limited differentiation between northern California and Oregon `r spp` populations indicating mixing between the areas. 

_Caveat_

Waples and Gaggiotti [@waples_what_2006]: Significant differences in neutral genetic characters indicate that the populations have been re-productively isolated for many generations,which is far longer than the ecological time scales that are relevant to stock assessment or fishery management.

<!---------------------------------------------------->

#### Variation in Phenotypic Traits

_Evidence for Managing at Assessment Scale_

Minor differences measured in maturity-at-length between two areas of the coast: Oregon [@hannah_length_2014] and South of Point Conception (Melissa Head, NWFSC). 

Punt et al.[-@punt_which_2015]: Conventional stock assessments produced significantly biased estimates when applied to an operating model of pink ling fisheries with spatial heterogeneity in fishing mortality, growth, and recruitment.

_Evidence for Alternative Management Scale_

Limited growth differences measured based on original age-length estimates between fish off the Oregon and Washington coast to those sample south of Point Conception. Caveat: Spatial gradients of growth across the coast are commonly observed in rockfish or other fish species along the U.S. west coast  [@keller_variation_2012; @gertseva_spatial_2017; @keller_canary_2018] and lack of measure growth variation may be due lack of spatial coverage of otoliths samples across the California coast.  

<!---------------------------------------------------->

### Other Considerations

#### Abundance Trends

_Evidence for Managing at Assessment Scale_

Ying et al. [-@ying_risks_2011]: The performance of stock assessments using an operating model to represent three connected sub-populations of small
yellow croaker and observed that assessing and managing each sub-population as a unit led to overfishing and managing the metapopulation
as a unit stock often led to local depletion.

The separate models for the areas south and north of Point Conception estimated two distinct stock trajectories with the stock in the north over recent years from low levels to at or around the management target and the stock in the south increasing from low levels between 2001 - 2014 and decreasing in recent years to levels below the minimum stock size threshold. The model for the area south of Point Conception did not estimate annual recruitment deviations which could contribute to stock trajectory differences to the stock to the north where strong recent recruitments have led to increases in stock size.  However, in the model sensitivity for the south of Point Conception model that estimated annual recruitment deviations the stock trajectory remaining low (below the minimum stock size threshold) and did not show similar stock increases as observed in the north. 

The trajectories across all model areas showed varying trajectories (Figure \ref{fig:depl-compare}). 


\clearpage

_Evidence for Alternative Management Scale_

The areas of true population variation in relative stock size may not align with the assessment boundaries as currently defined. State based management is likely not the only factor impacting relative stock sizes across the coast where movement and recruitment patterns likely also influence potential differences in relative stock size.  

Cope and Punt [-@cope_data-moderate_2013]: Conventional stock assessments failed to estimate differing spatial patterns and exploitation (localized depletion) but adequately estimated the overall stock status. 



<!---------------------------------------------------->

#### Size and Age Composition   

_Evidence for Managing at Assessment Scale_

Distinct selectivity curves estimated between the recreational and commercial fisheries north and south of Point Conception.  While to a lesser degree, the selectivity in Oregon and Washington commercial and recreation fleets also varied from selectivity estimated in other areas.

Bosely et al. [-@bosley_overcoming_2019]: Specifying the correct form spatial population structure may not e as critical as understanding movement patterns and spatial heterogeneity in fishery selectivity and life-history variation when developing reference points for management. 

Berger et al. [-@berger_incoherent_2021]: Aligning management assessment areas with  with underlying population
structure and processes is important, especially when fishing mortality is disproportionate to vulnerable biomass among management areas, demographic parameters (growth and maturity) are not homogeneous within management areas, and connectivity (via recruitment or movement) unknowingly exists among management areas. Bias and risk were greater for assessments that incorrectly span multiple population segments compared to assessments that cover a subset of a population segment, and these results were exacerbated when there was connectivity between population segments. Caveat: The variation is growth and connectivity between areas via recruitment for `r spp` off the West Coast is currently unknown or uncertain. 


_Caveat_

Rather than creating separate assessments to account for variation in exploitation or life-history variation across areas a more integrated approach could be to apply a spatial assessment that can provide both area- and coastwide population estimates. However, spatial assessments come at the cost of a larger number of parameters to estimate, but general guidance around the key decisions exists when moving to spatial assessments (Punt [-@punt_spatial_2019]). This approach should be evaluated to understand the trade-offs between adding parameters that may be poorly informed (e.g., movement, recruitment by area) via a spatial assessment approach versus either conducting separate assessments or applying the "fleets-as-areas" approach.  

\clearpage

